---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rjd3toolkit

<!-- badges: start -->
[![R-CMD-check](https://github.com/rjdemetra/rjd3toolkit/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rjdemetra/rjd3toolkit/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->


Utility package in JDemetra+ 3.x R ecosystem. Contains utility functions used in other `rjd3` packages and has to be systematically installed before using any other rjd3 package. 

## Main Functions 

-   customize specifications in rjd3x13 and rjdtramoseats

-   generate user-defined regressors for calendar correction

-   generate auxiliary variables (outliers, ramps..)

-   run arima model estimations

-   perform tests (seasonality, normality, white noise)

-   access general functions such as auto-correlations, distributions


## Installation

Running rjd3 packages requires Java 17 or higher. How to set up such a configuration in R is explained [here](https://jdemetra-new-documentation.netlify.app/#installing-the-software).

To get the current stable version (from the latest release):

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3toolkit@*release")
```

To get the current development version from GitHub:

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3toolkit")
```


## Package Maintenance and contributing

Any contribution is welcome and should be done through pull requests and/or issues.
pull requests should include **updated tests** and **updated documentation**. If functionality is changed, docstrings should be added or updated.


## Licensing

The code of this project is licensed under the [European Union Public Licence (EUPL)](https://joinup.ec.europa.eu/collection/eupl/eupl-text-eupl-12).
